### 2021-07-22 manuscript.tex
Cleaning debt, but still a lot left ☹

Although studies of FGC norms were abundant \cf{seems too strong. a better word than that?} as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.  Such information adds depth to understanding the wax and wane of FGC practice.  We believe this is the first FGC study using normative attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention).

@@

In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and geographic estimates of community FGC prevalence.  The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!} in their community. We used index of attitudinal evaluation of FGC benefits to represent FGC norm.  Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13 , PashPonn16, ShelHern06,}} \cfonly{check cites}.  However, there has bee little quantitative research on the relationship between attitudes and intention of cutting daughters at both an individual and community level incorporating beliefs of FGC benefits.

@@

Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{Makie etc} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.  The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).  We propose that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.  The similar coordination also applied to supporting FGC practice in the future.  The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}. \cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?  What can we find from the benefits PCAs?}.  \cfonly{Need to add Hayf05}

@@

Although FGC prevalence was a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status. In this case, what people did (descriptive norm?) was less a force than what they will do.  In other words, - descriptive norm (i.e., FGC prevalence) was undermined by subjective norm (community intentional behaviour of . \cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.  Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.   FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19 (confirm), ShelWand11} (more)

@@

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cr{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).

The positive impact modernization \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02} on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded \cite{Hayf05} \cfonly{to confirm}. While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite, Hayf05}.

@@

It is noticed that the patterns of FGC benefits based on the PCA results \cfml\{PCA figures} indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.  The main index was grouped as others.  It means that the main reasons of why mothers intended to cut their daughters or what they believe was the real benefits/reason was not clearly stated. It could be reasons aforementioned as, for example, peer convention \cite{GrosHayd19 (confirm), ShelWand11}.  Further field research is recommended to further clarify reasons of cutting.

@@

- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}; medicalizing FGC \cite{LeyeVanE19}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \ciet{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs. trickle-down strategy)
- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html). Both human rights deliberation and coordinated community abandonment are necessary for change. National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level. “ (use \cite{Dagn09, MackLeJe08} for this idea)
- a bottom-up intervention aimed at changing social expectation \cite{BiccMari15}
- Instead of focusing on improving knowledge and changing attitudes, we need to be more cautious about implementation of social norm interventions and infuse intervention in a relational dimension and a dynamic framework \cite{CislHeis18a, CislHeis18b, McCh15}.  Empowering local community and opinion leaders in implementing “organized diffusion” \cite{MackLeJe08}has proven cost-effective \cite{CislDenn19}. (and Boston?)

@@

— Limitation —
While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?  As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cit{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.

- No FGC types relating to our response variables
- Not controlling for daughter’s age
- Not considering heterogeneity.

@@

% The finding “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models … , wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

% "Tradition, cleanliness, and virginity were the most common motives empowering the continuation of FGM/C , followed by men's wish, esthetic factors, marriage, and religion factors.... A variety of socio-cultural myths, religious misbelievers, and hygienic and esthetic concerns were behind the FGM/C. Overall, a large proportion of the participants supported the continuation of FGM/C in spite of adverse effect and sexual dysfunction associated with FGM/C." \cite{MohaHass14}

>>>>

Although studies of FGC norms were abundant \cfcmt{seems too strong. a better word than that?} as aforementioned, there was limited analysis of how individual normative attitudes (e.g., attitudinal position of FGC values) and behavioural intention intertwining with the group norm.  Such information adds depth to understanding the wax and wane of FGC practice.  We believe this is the first FGC study using normative attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention).

@@

In this study, we focused on women’s intention of whether they will have their daughter’s genital modified in the context of group FGC norms and geographic estimates of community FGC prevalence.  The research presumption was based on the studies aforementioned that women’s intention on practicing FGC on their daughters was dependent on other women’s intention of this practice \cfonly{descriptive norms?!} in their community. We used index of attitudinal evaluation of FGC benefits to represent FGC norm.  Attitudes is a sensible proxy of social norm \cfonly {norm theory \cite{Ajze91, Ajze02, Bicc10, BiccMari15, Mack96, Mack00, MackLeJe08, RimaLapi15, Youn11} and has been applied on fgc studies \cite{CislHeis18, EffeVogt15, Harf06, ModrLiu13, PashPonn16, ShelHern06,}} \cfonly{check cites}.  However, there has bee little quantitative research on the relationship between attitudes and intention of cutting daughters at both an individual and community level incorporating beliefs of FGC benefits.

@@

Based on the findings which rebutted a previous study \cite{EffeVogt15}, we believed that FGC is a social coordinated norm \cite{MakieETC} in the studied countries (Kenya, Mali, Nigeria and Sierra Leon):  an individual behavioral intention is subjected to the normative ritual in their community.  The norm of FGC is synergistic, based on what women think about other women’s likely position in their community (i.e., likelihood of others to cut their daughters) and values they attached to this practice (i.e., beliefs of FGC benefits).  We propose that a mother’s intention of cutting their daughters was overdetermined by her community’s overall intention to cut daughters and her personal beliefs of FGC benefits more than her own fgc status and FGC prevalence in the community (see daughrer isoplot x and effect plots x)\cf{Can we use some stat to elaborate our argument?}.  The similar coordination also applied to supporting FGC practice in the future.  The coordinated performance could (or would be?) be a result of subjective norm as perceived social pressure to perform such behaviour or expected choice of conduct \cite{Ajze91}. \cfonly{FGC is less a coordination rite than singling group identity and symbolism \cite{ShelWand11, Youn15}} \cf{But what is this coordination based on if not marriageability?  What can we find from the benefits PCAs?}.  \cfonly{Need to add Hayf05}

@@

Although FGC prevalence was a main factor predicting daughter’s FGC status \cite{BoylSvec19} \cf{more cites}, we found that overall community intention explained more variance than FGC prevalence on respondents’ intention of cutting daughters cfonly{ show daughter effect plot}:  What their community members will do is likely to determine what a mother intends to do with their daughters’ FGC status. In this case, what people did (descriptive norm?) was less a force than what they will do.  In other words, - descriptive norm (i.e., FGC prevalence) was undermined by subjective norm (community intentional behaviour of . \cf{One confusing finding is that all the three models showed group fgc benefits are robustly and negatively associated with the responses.}.  Norms sustained through communications and evolve through social interactions \cite{FishAjze10, RimaLapi15}.   FGC is conventional \cite{FreyJohn07, Hayf05, KandShel19, Mack96, ShelWand11} which may evolve into various forms of conventional norms, such as peer convention \cite{GrosHayd19CONFIRM, ShelWand11} (more)

@@

Our models showed that the four countries were clearly different in intention of cutting their daughters with Sierra Lion of the highest likelihood and Nigeria compared to FGC prevalence where Sierra Leon had the highest prevalence, followed by Mali, Nigeria and Kenya; yet their attitudes of supporting FGC practice was not clear despite the factor of FGC prevalence \cf{figure xx and figure xxx}.  Regarding sociodemographic factors, education (community), wealth (individual and community) and job (individual) did not predict women’s intention on cutting their daughters, nor did gender awareness (community).

The positive impact modernization \cite{BoylMcMo02, Youn02} and gender/feminist perspectives \cite{BoylSvec19, DalaLawo10, Dell04, FrieMahm13, KandNwak09, Lewi04, Meye00, Njam04, YirgKass12, Youn02} on intention of cutting daughters were not obvious than the convention approach in our findings as well as previously concluded \cite{Hayf05} \cfonly{to confirm}. While a daughter’s FGC risk was higher if she was in a community with a higher community-level of women’s extra familial opportunities (e.g., education, paid work and marital background) \cite{GrosHayf19}, our findings showed that community level of education was not a clear determinant of daughter’s FGC risk, compare to a previous study showed that community education had no clear effect on the likelihood of daughter’s FGC future, while the individual education did in Kenya \cite{Hayf05}.

@@

It is noticed that the patterns of FGC benefits based on the PCA results \cfcmt{M: PCA figures} indicated that benefits of FGC was not as clearly elaborated as the benefit module categorized.  The main index was grouped as others.  It means that the main reasons of why mothers intended to cut their daughters or what they believe was the real benefits/reason was not clearly stated. It could be reasons aforementioned as, for example, peer convention \cite{GrosHayd19CONFIRM, ShelWand11}.  Further field research is recommended to further clarify reasons of cutting.

@@

- MC vs. FGC.  Considering the acceptance of Alternative rights of passage \cite{GaluKama15} without criminalize the practice. (I'm not sure if I'm comfortable with this position, but it is an alternative.) vs. focused on empowerment, and campaigns to recruit change agents from within communities (to eradicate FGC) \cite{ShelHern13, Will18}; medicalizing FGC \cite{LeyeVanE19}
- modelling by plotting empirical data to study threshold/tipping point.
- redesign questions of fgc benefits in DHS
- inviting faced women migrated to western society to participate in fgc intervention campaign.  For example,  attitude change: "migrating to and living in Sweden facilitates a transition in attitudes regarding FGC" \cite{WahlJohn17}, and initiating “participatory campaign and education”  (an idea from \cite{MackLeJe08}’s “participatory human rights education” and Boston’s), including women’s empowerment and horizontal involvement (vs. trickle-down strategy)
- \cite{MackLeJe08}”coordinated community abandonments (Dagne 2008, http://www.kmgselfhelp.org/hotissues.html). Both human rights deliberation and coordinated community abandonment are necessary for change. National programmes in Egypt and Sudan are promoting positive human rights messages and discussions at national, regional, and local levels, and are experimenting with a variety of coordinated abandonment through community dialogue efforts at the local level. “ (use \cite{Dagn09, MackLeJe08} for this idea)
- a bottom-up intervention aimed at changing social expectation \cite{BiccMari15}
- Instead of focusing on improving knowledge and changing attitudes, we need to be more cautious about implementation of social norm interventions and infuse intervention in a relational dimension and a dynamic framework \cite{CislHeis18a, CislHeis18b, McCh15}.  Empowering local community and opinion leaders in implementing “organized diffusion” \cite{MackLeJe08}has proven cost-effective \cite{CislDenn19}. (and Boston?)

@@

— Limitation —
While beliefs of FGC benefits was a clear factor associating with women’s intention of cutting their daughters, our findings could not clarify what benefits exactly the women believed?  As proposed that social norm and the behavior it compels cannot be inferred from personal attitude \cite{Mack18} (in rebuttal letter), a further analysis to entangle the FGC beliefs is expected.

- No FGC types relating to our response variables

- Not controlling for daughter’s age

- Not considering heterogeneity.

@@

% The finding “suggests that even with a sharp decrease in FGC prevalence, the bulk of FGC persistence would still come from household-level factors. This is in contrast to the tipping point and informational cascade models …, wherein the decision to abandon a social norm such as FGC should be entirely individual in places where the practice is highly pervasive.”  they found that “that much of the variation in a woman's support for FGC can be attributed to individual- and household-level factors rather than to village-level factors or to factors beyond the village level”  \cite{BellNova15}; and to compare our results to \cite{BellNova15} because they agnostic about the three theories.

@@

% "Tradition, cleanliness, and virginity were the most common motives empowering the continuation of FGM/C, followed by men's wish, esthetic factors, marriage, and religion factors.... A variety of socio-cultural myths, religious misbelievers, and hygienic and esthetic concerns were behind the FGM/C. Overall, a large proportion of the participants supported the continuation of FGM/C in spite of adverse effect and sexual dysfunction associated with FGM/C." \cite{MohaHass14}
